\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
Discussion: added commas

    More in detail, we have also found that the impact of contaminant deprojection on the covariance matrix, through the corresponding loss of modes, is negligible unless a very large number of contaminant templates are removed. This simplifies the procedure to estimate covariance matrices for galaxy clustering data, which are particularly sensitive to a large number of astrophysical and observational systematics. Additionally, we have found that, although the NKA estimator is accurate enough, it is not able to perfectly capture the additional effects of mode coupling that are present for spin-2 fields, and that a simpler approach treating the shear $E$ modes as a spin-0 object is able to reach similar levels of accuracy. Due to the imperfect treatment of the $E/B$ mixing caused by the sky mask in the NKA estimator, we also find that the predicted covariance matrix for any power spectra involving $B$ modes differs significantly from the true sample covariance, and therefore this approach cannot be used to reliably estimate the uncertainties of $B$-mode power spectra. Likewise, we find that the NKA estimator yields inaccurate estimates of the power spectrum uncertainties on the largest scales ($\ell\lesssim50$). Although these modes carry a substantially smaller statistical weight, if more accurate covariances are needed on these large scales, they can be easily computed making use of fast low-resolution simulations.

    In spite of these shortcomings, we find that the approximations described in this paper are able to provide estimates of the power spectrum covariance matrix that are sufficiently accurate for current and future tomographic large-scale structure cosmological datasets. The main advantage of this approach is the computational cost, which is comparable to that of estimating the power spectrum in the first place, and which scales with pixel resolution in a similar way. This is therefore significantly less time-consuming than generating large numbers of mock datasets (even simple Gaussian or log-normal realizations), and more reliable than the traditional jackknife resampling techniques. The method, in all its generality, is currently implemented in the public code {\tt NaMaster}. Future extensions to this work will focus on improving the estimator for power spectra involving $B$ modes, and incorporating the impact of $E/B$-mode purification \cite{2002PhRvD..65b3505L,2003PhRvD..67b3501B,2006PhRvD..74h3002S}.

>>>>

    More in detail, we have also found that the impact of contaminant
    deprojection on the covariance matrix, through the corresponding loss of
    modes, is negligible unless a very large number of contaminant templates
    are removed. This simplifies the procedure to estimate covariance matrices
    for galaxy clustering data, which are particularly sensitive to a large
    number of astrophysical and observational systematics. Additionally, we
    have found that, although the NKA estimator is accurate enough, it is not
    able to perfectly capture the additional effects of mode coupling that are
    present for spin-2 fields, and that a simpler approach treating the shear
    $E$ modes as a spin-0 object is able to reach similar levels of accuracy.
    Due to the imperfect treatment of the $E/B$ mixing caused by the sky mask
    in the NKA estimator, we also find that the predicted covariance matrix
    for any power spectra involving $B$ modes differs significantly from the
    true sample covariance, and, therefore, this approach cannot be used to reliably estimate the uncertainties of $B$-mode power spectra. Likewise, we find that the NKA estimator yields inaccurate estimates of the power spectrum uncertainties on the largest scales ($\ell\lesssim50$). Although these modes carry a substantially smaller statistical weight, if more accurate covariances are needed on these large scales, they can be easily computed making use of fast low-resolution simulations.

    In spite of these shortcomings, we find that the approximations described
    in this paper are able to provide estimates of the power spectrum
    covariance matrix that are sufficiently accurate for current and future
    tomographic large-scale structure cosmological datasets. The main
    advantage of this approach is the computational cost, which is comparable
    to that of estimating the power spectrum in the first place, and which
    scales with pixel resolution in a similar way. This is, therefore, significantly less time-consuming than generating large numbers of mock datasets (even simple Gaussian or log-normal realizations), and more reliable than the traditional jackknife resampling techniques. The method, in all its generality, is currently implemented in the public code {\tt NaMaster}. Future extensions to this work will focus on improving the estimator for power spectra involving $B$ modes, and incorporating the impact of $E/B$-mode purification \cite{2002PhRvD..65b3505L,2003PhRvD..67b3501B,2006PhRvD..74h3002S}.
